---
title: "p8105_hw1_rw3031"
author: "Polly Wu (rw3031)"
date: "2024-09-12"
output: github_document
---

# Problem 1

I installed the package palmerpenguins. 

## Describe the penguin dataset
```{r}
data("penguins", package = "palmerpenguins")
str(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```
There are 8 variables in the penguin dataset. Species is a factor variable with 3 levels, island is a factor variable with 3 levels, bill_length_mm is a numeric variable, flipper_length_mm is a numeric variable, body_mass_g is a numeric variable, sex is a factor with 2 levels, and year is a numeric variable. 
The penguins data set contains 8 columns and 344 rows. 
The mean flipper length is 200.9152.

## Scatterplot 
```{r}
library(ggplot2)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```

# Problem 2

## Create the data frame
```{r}
library(tidyverse)
```

```{r}
df_p2 = tibble(
  random_value = rnorm(n=10, mean=1),
  value_positive = random_value>0,
  char = c("a","b","c","d","e","f","g","h","i","j"),
  factor = c("level1", "level2","level3", "level1", "level2", "level3","level1", "level2", "level3", "level1")
  )
```

## Obtain the mean of the variables 
```{r}
mean(pull(df_p2,random_value))
mean(pull(df_p2,value_positive))
mean(pull(df_p2,char))
mean(pull(df_p2,factor))
```
We can only obtain the mean for logical and numeric variables. 
For character and factor variables, we cannot obtain their mean. 

## Convert to numeric
```{r eval=FALSE}
as.numeric(pull(df_p2,value_positive))
as.numeric(pull(df_p2,char))
as.numeric(pull(df_p2,factor))
```
The transformation of the character and factor variables return NA. 
